Titeln på avhandlingens språk

### 2023-02-03 model.tex
thesis tweaks

Apart from the aforementioned timing and performance data, for~\cite{olguinmunoz:impact2021} we also recorded all collected video frame samples together with matching metadata.
For each video frame submitted to the \gls{WCA} during the tasks, we recorded
\begin{enumerate*}[itemjoin={{; }}, itemjoin*={{; and }}]
    \item the raw video frame captured
    \item sample submission timestamp
    \item \gls{WCA} processing completed timestamp
    \item result or acknowledgement returned timestamp
    \item a tag representing the result of the \gls{WCA} processing
\end{enumerate*}.
The tags assigned corresponded to:
\begin{description}[font={\bfseries\ttfamily}, wide]
    \item[SUCCESS:] frames which triggered a transition to a new step (or the correction of a previous mistake) in the logical task model of the \gls{WCA}, and thus cause the generation of feedback to the user.
    \item[REPEAT:] frames which captured the same board state as the previous successful frame, and thus produced no feedback.
    \item[LOW\_CONFIDENCE] frames for which the image recognition algorithm in the \gls{WCA} did not reach the necessary confidence threshold to interpret it as a valid board state.
        These frames also produce no feedback.
    \item[BLANK] frames in which not enough of the board is visible due to noise, movement, occlusion, etc.
        These frames produce no feedback either.
    \item[TASK\_ERROR] frames which contained an incorrect board state and thus triggered a transition to a procedural corrective step and the generation of feedback to the user.
        However, it must be noted that none of the \num{40} participants made any mistakes during the task, and thus no such frames were encountered in the data.
\end{description}

@@

Using the above insights, together with the corresponding recorded video frames, we devise a scheme for the procedural generation of a synthetic trace for any step in \gls{WCA} task in the same category as those used in~\cite{olguinmunoz:impact2021}.
We first prepare a discretized representation of the probability density map in \cref{fig:frameprobs}.
We segment the normalized instant value into a number of discrete bins (\num{25} in this work), and calculate the relative fraction of frames for each category in each bin.
For each step, given
\begin{enumerate*}[itemjoin={{; }}, itemjoin*={{; and }}]
    \item a collection of random non-\texttt{SUCCESS}, non-\texttt{REPEAT} frames (at least one frame for each of the \texttt{BLANK} and \texttt{LOW\_CONFIDENCE} categories)
    \item an appropriate \texttt{SUCCESS} video frame containing the correct state for the step
    \item an appropriate \texttt{REPEAT} video frame containing the correct state for the \emph{previous} step
\end{enumerate*},
we can then procedurally generate a trace by randomly selecting appropriate frames according to the distributions presented in \cref{fig:frameprobs}.
In other words, for each sampling instant in a step with a given execution time \( t_\text{exec} \):
\begin{enumerate}
    \item We calculate \( t_\text{norm} \) according to \cref{eq:tnorm}.
    \item If \( t_\text{norm} \ge 1.0 \), we select the \texttt{SUCCESS} frame and stop sampling.
    \item If instead \( t_\text{norm} < 1.0 \), we find the appropriate bin for \( t_\text{norm} \) and then select a frame by performing a weighted random sampling of the frame categories in the normalized instant bin.
\end{enumerate}

>>>>

Apart from the aforementioned timing and performance data, for~\cite{olguinmunoz:impact2021} we also recorded all collected video frame samples together with matching metadata.
For each video frame submitted to the \gls{WCA} during the tasks, we recorded
\begin{inlineenum}
    \item the raw video frame captured
    \item sample submission timestamp
    \item \gls{WCA} processing completed timestamp
    \item result or acknowledgement returned timestamp
    \item a tag representing the result of the \gls{WCA} processing
\end{inlineenum}.
The tags assigned corresponded to:
\begin{description}[font={\bfseries\ttfamily}, wide]
    \item[SUCCESS:] frames which triggered a transition to a new step (or the correction of a previous mistake) in the logical task model of the \gls{WCA}, and thus cause the generation of feedback to the user.
    \item[REPEAT:] frames which captured the same board state as the previous successful frame, and thus produced no feedback.
    \item[LOW\_CONFIDENCE] frames for which the image recognition algorithm in the \gls{WCA} did not reach the necessary confidence threshold to interpret it as a valid board state.
        These frames also produce no feedback.
    \item[BLANK] frames in which not enough of the board is visible due to noise, movement, occlusion, etc.
        These frames produce no feedback either.
    \item[TASK\_ERROR] frames which contained an incorrect board state and thus triggered a transition to a procedural corrective step and the generation of feedback to the user.
        However, it must be noted that none of the \num{40} participants made any mistakes during the task, and thus no such frames were encountered in the data.
\end{description}

@@

Using the above insights, together with the corresponding recorded video frames, we devise a scheme for the procedural generation of a synthetic trace for any step in \gls{WCA} task in the same category as those used in~\cite{olguinmunoz:impact2021}.
We first prepare a discretized representation of the probability density map in \cref{fig:frameprobs}.
We segment the normalized instant value into a number of discrete bins (\num{25} in this work), and calculate the relative fraction of frames for each category in each bin.
For each step, given
\begin{inlineenum}
    \item a collection of random non-\texttt{SUCCESS}, non-\texttt{REPEAT} frames (at least one frame for each of the \texttt{BLANK} and \texttt{LOW\_CONFIDENCE} categories)
    \item an appropriate \texttt{SUCCESS} video frame containing the correct state for the step
    \item an appropriate \texttt{REPEAT} video frame containing the correct state for the \emph{previous} step
\end{inlineenum},
we can then procedurally generate a trace by randomly selecting appropriate frames according to the distributions presented in \cref{fig:frameprobs}.
In other words, for each sampling instant in a step with a given execution time \( t_\text{exec} \):
\begin{enumerate}
    \item We calculate \( t_\text{norm} \) according to \cref{eq:tnorm}.
    \item If \( t_\text{norm} \ge 1.0 \), we select the \texttt{SUCCESS} frame and stop sampling.
    \item If instead \( t_\text{norm} < 1.0 \), we find the appropriate bin for \( t_\text{norm} \) and then select a frame by performing a weighted random sampling of the frame categories in the normalized instant bin.
\end{enumerate}

### 2023-02-03 sampling.tex
thesis tweaks

Now, if we have a constrained optimization with an upper bound $w_0$ for the expected wait time, we can find the optimum set of sampling instants by equating \cref{Ew} to $w_0$ and find the ratio of $\frac{\alpha}{\beta}$ that provides the optimum set of sampling instants when plugged into \cref{tnFinal}.
For this, we make use of the facts that
\begin{enumerate*}[itemjoin={{, }}, itemjoin*={{, and }}]
    \item the bound will be tight at the optimum due to the continuous nature of possible sampling instants and sampling intervals
    \item one can achieve any arbitrary point $(\mathbb{E}[\mathcal{S}],\mathbb{E}[\mathcal{W}])$ via the unconstrained optimization discussed above simply by varying the ratio $\frac{\alpha}{\beta}$.
\end{enumerate*}
\begin{alignat*}{1}
\mathbb{E}[\mathcal{W}]&=\int_{0}^{\infty}\dfrac{1}{2r(t)}f_\mathcal{T}(t)\,\mathrm{d}t.\nonumber\\
&=\int_{0}^{\infty}\frac{1}{2}\sqrt{\frac{2\alpha\sigma^2}{\beta t}}\cdot \frac{t}{\sigma^2}e^{-{t^2}/{2\sigma^2}}\mathrm{d}t\\
&=\sqrt{\frac{\alpha\sigma^2}{2\beta}}\int_{0}^{\infty}\frac{\sqrt{t}}{\sigma^2}e^{-{t^2}/{2\sigma^2}}\mathrm{d}t\\
&=\sqrt{\frac{\alpha\sigma^2}{2\beta}}\left({\frac{1}{{2}\sigma^2}}\right)^{1/4}\cdot\int_{0}^{\infty}y^{-1/4}e^{-y}\mathrm{d}y\\
&=\sqrt{\frac{\alpha\sigma^2}{2\beta}}\left({\frac{1}{{2}\sigma^2}}\right)^{1/4}\cdot\mathlarger{\Gamma}(\tfrac{3}{4})\\
% &\approx 0.728637\sqrt{\frac{\alpha\sigma}{\beta}}\\
\intertext{Thus, when the upper bound $w_0$ is tight,}
w_0&=0.728637\sqrt{\frac{\alpha\sigma}{\beta}}\\
w_0&=\sqrt{\frac{\alpha\sigma}{2\sqrt{2}\beta}}\mathlarger{\Gamma}(\tfrac{3}{4})\\
\Rightarrow\frac{\alpha}{\beta}&=\frac{w_0^2}{\sigma}\frac{2\sqrt{2}}{(\mathlarger{\Gamma}(\tfrac{3}{4}))^2}\\&=1.88355\frac{w_0^2}{\sigma}
\end{alignat*}

By making use of this general solution, we can also prove the results given in section \ref{sec:aprxSol_Energy_samples}, where we modify the problem and find the optimum sampling instants that minimises the expected number of samples for a given upper bound $w_0$ for the expected wait time. 
First note that, the general solution has constants $\alpha$ and $\beta$ that corresponds to the weights given to the cost of sampling and cost of waiting, respectively. The optimisation criteria changes from minimising wait time to minimising the number of samples, when the ratio $\frac{\alpha}{\beta}$ goes from zero to infinity. Since any positive real value is valid for this ratio, and since the sampling instants are aperiodic and can take any positive real values, we have
\begin{enumerate*}
    \item the bound will be tight at the optimum due to the continuous nature of possible sampling instants and sampling intervals
    \item one can achieve any arbitrary point $(\mathbb{E}[\mathcal{S}],\mathbb{E}[\mathcal{W}])$ via the unconstrained optimization discussed above simply by varying the ratio $\frac{\alpha}{\beta}$.
\end{enumerate*}
Thus, can argue that any optimisation problem -- constrained or unconstrained -- can be boiled down to modifying the problem to the general format and finding the appropriate $\frac{\alpha}{\beta}$ ratio. Hence, to solve for the modified optimisation problem explained in section \ref{sec:aprxSol_Energy_samples} that minimises $(\mathbb{E}[\mathcal{S}]$ with an upper bound $w_0$ on $(\mathbb{E}[\mathcal{W}]$, we equate \cref{Ew} to $w_0$, find the corresponding $\frac{\alpha}{\beta}$ and find the optimum set of sampling instants by plugging this ratio into \cref{tnFinal}.

>>>>

Now, if we have a constrained optimization with an upper bound $w_0$ for the expected wait time, we can find the optimum set of sampling instants by equating \cref{Ew} to $w_0$ and find the ratio of $\frac{\alpha}{\beta}$ that provides the optimum set of sampling instants when plugged into \cref{tnFinal}.
For this, we make use of the facts that
\begin{inlineenum}
    \item the bound will be tight at the optimum due to the continuous nature of possible sampling instants and sampling intervals
    \item one can achieve any arbitrary point $(\mathbb{E}[\mathcal{S}],\mathbb{E}[\mathcal{W}])$ via the unconstrained optimization discussed above simply by varying the ratio $\frac{\alpha}{\beta}$.
\end{inlineenum}
\begin{alignat*}{1}
\mathbb{E}[\mathcal{W}]&=\int_{0}^{\infty}\dfrac{1}{2r(t)}f_\mathcal{T}(t)\,\mathrm{d}t.\nonumber\\
&=\int_{0}^{\infty}\frac{1}{2}\sqrt{\frac{2\alpha\sigma^2}{\beta t}}\cdot \frac{t}{\sigma^2}e^{-{t^2}/{2\sigma^2}}\mathrm{d}t\\
&=\sqrt{\frac{\alpha\sigma^2}{2\beta}}\int_{0}^{\infty}\frac{\sqrt{t}}{\sigma^2}e^{-{t^2}/{2\sigma^2}}\mathrm{d}t\\
&=\sqrt{\frac{\alpha\sigma^2}{2\beta}}\left({\frac{1}{{2}\sigma^2}}\right)^{1/4}\cdot\int_{0}^{\infty}y^{-1/4}e^{-y}\mathrm{d}y\\
&=\sqrt{\frac{\alpha\sigma^2}{2\beta}}\left({\frac{1}{{2}\sigma^2}}\right)^{1/4}\cdot\mathlarger{\Gamma}(\tfrac{3}{4})\\
% &\approx 0.728637\sqrt{\frac{\alpha\sigma}{\beta}}\\
\intertext{Thus, when the upper bound $w_0$ is tight,}
w_0&=0.728637\sqrt{\frac{\alpha\sigma}{\beta}}\\
w_0&=\sqrt{\frac{\alpha\sigma}{2\sqrt{2}\beta}}\mathlarger{\Gamma}(\tfrac{3}{4})\\
\Rightarrow\frac{\alpha}{\beta}&=\frac{w_0^2}{\sigma}\frac{2\sqrt{2}}{(\mathlarger{\Gamma}(\tfrac{3}{4}))^2}\\&=1.88355\frac{w_0^2}{\sigma}
\end{alignat*}

By making use of this general solution, we can also prove the results given in section \ref{sec:aprxSol_Energy_samples}, where we modify the problem and find the optimum sampling instants that minimises the expected number of samples for a given upper bound $w_0$ for the expected wait time. 
First note that, the general solution has constants $\alpha$ and $\beta$ that corresponds to the weights given to the cost of sampling and cost of waiting, respectively. The optimisation criteria changes from minimising wait time to minimising the number of samples, when the ratio $\frac{\alpha}{\beta}$ goes from zero to infinity. Since any positive real value is valid for this ratio, and since the sampling instants are aperiodic and can take any positive real values, we have
\begin{inlineenum}
    \item the bound will be tight at the optimum due to the continuous nature of possible sampling instants and sampling intervals
    \item one can achieve any arbitrary point $(\mathbb{E}[\mathcal{S}],\mathbb{E}[\mathcal{W}])$ via the unconstrained optimization discussed above simply by varying the ratio $\frac{\alpha}{\beta}$.
\end{inlineenum}
Thus, can argue that any optimisation problem -- constrained or unconstrained -- can be boiled down to modifying the problem to the general format and finding the appropriate $\frac{\alpha}{\beta}$ ratio. Hence, to solve for the modified optimisation problem explained in section \ref{sec:aprxSol_Energy_samples} that minimises $(\mathbb{E}[\mathcal{S}]$ with an upper bound $w_0$ on $(\mathbb{E}[\mathcal{W}]$, we equate \cref{Ew} to $w_0$, find the corresponding $\frac{\alpha}{\beta}$ and find the optimum set of sampling instants by plugging this ratio into \cref{tnFinal}.
